---
title: "Usage"
output: html_notebook
---

### Reading data from the compression report
The main purpose of this program is to provide (for me) a simple way to compress large bunch of folders which contain a lot of files.
The compression report is a csv file which contains the following columns:

- `name`: the name of the file
- `input_path`: path of the original file
- `output_path`: path of the compressed file
- `original_size`: the original size of the file
- `compressed_size`: the compressed size of the file
- `saved_storage`: the saved storage we got from the compression
- `percent`: the percentage of the saved storage

```{r}
data <- read.csv("./example/compression_report_2024-02-01_02-47-12.csv")
data
```

Each file that has been compressed will be logged into a history file. This history file is a csv file which contains the following columns:

- `path`: the path of the original file
- `is_compressed`: a boolean value which indicates if the file has been compressed or not
- `compression_level`: the compression level represents the quality of the compression. The higher the compression level, the better the compression quality. The compression level is an integer between 0 and 9.

```{r}
data <- read.csv("./example/history.csv")
data
```